Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-11 paper/paper.tex
Muck around with the graphs a bit, add some FC

    \centering
    \input{gen-graph-unconnected-heatmap}
    \caption{The cumulative number of instances solved in under a certain time: on the top, 33\%
        labelled graphs with up to 100 vertices, and in the middle, unlabelled and undirected graphs
        with up to 35 vertices. On the bottom row, an instance-by-instance comparison of the two
        models, with 33\% labelled graphs on the left, and unlabelled and undirected graphs on
        the right.} \label{figure:unconnected-cumulative}
\end{figure}

>>>>

    \centering
    \input{gen-graph-unconnected-heatmap}
    \caption{The cumulative number of instances solved in under a certain time: on the top, 33\%
        labelled graphs with up to 100 vertices, and in the middle, unlabelled and undirected graphs
        with up to 35 vertices. On the bottom row, an instance-by-instance comparison of the clique
        model with the best CP model, with 33\% labelled graphs (with MAC) on the left, and
        unlabelled and undirected graphs (with FC) on the right.} \label{figure:unconnected-cumulative}
\end{figure}
